### 2018-12-14 Chapters/Chapter2.tex
changes

In the absence of spin-orbit interaction the model \ref{Hubbard} becomes the well-known Hubbard model: $\hat{H} = -\sum_{\langle i,j \rangle, \sigma} t_{ij} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$. This model has been extensively studied since its proposal in 1963 by Hubbard \cite{Hubbard1963}. Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it. Originally the Hubbard model was proposed to describe electron correlations in a simplified way and to predict metal-insulator transitions. It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory. Also, the attractive Hubbard model (where $\text{U} < 0$) is relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.

>>>>

In the absence of spin-orbit interaction the model \ref{Hubbard} becomes the well-known Hubbard model: $\hat{H} = -\sum_{\langle i,j \rangle, \sigma} t_{ij} \hat{c}_{i \sigma}^\dagger \hat{c}_{j \sigma} + \text{U} \sum_{i=1}^M \hat{n}_{i\uparrow}\hat{n}_{i\downarrow}$. This model has been extensively studied since its proposal in 1963 by Hubbard \cite{Hubbard1963}. Despite its simplicity the ground state has no analytic form in more than one dimensions, and different computational methods must be used to study it. Originally the Hubbard model was proposed to describe electron correlations in $d$ or $f$ bands in transition metals. The result was a simplified model to predict metal-insulator transitions. However, it exhibits much richer phenomena. It can be considered an impoved tight binding model, describing Mott insulators, which cannot be describied by band theory (i.e. they should be conductors according to band theory, but electron-electron interactions keep away from). Also, the attractive Hubbard model (where $\text{U} < 0$) can be considered an effective model relevant for understanding high temperature superconductivity \cite{Alexandrov1981}.
